\documentclass{article}

\usepackage[margin=1.5in]{geometry}
\usepackage[dvipsnames]{xcolor}

\title{Market Research for "Sadabahar"}
\author{Krishna Agrawal, 19111031}
\date{\today}

\begin{document}
\maketitle

\section*{Abstract}

In this term paper, I have done market research for indoor plant industry, presented insights about indoor plants and their benefits. I have also covered the various business model possible and at last presented customer insight from the survey done. Eventually i have tried to come up with a Business Model for our venture.


\section*{Introduction}

Sadabahar is a one stop solution for all Indoor Plant Lovers. We provide complete support for Indoor Plants. Our services don't end when a customer buys a plant, it just starts from there. We accompany our customers in the journey of growing their plant and help them in keeping their plant alive Sadabahar with them! 

With the advent of pandemic, people have been more cautious on their life, health and mental health too. People are finding ways to improve their mental peace and have started turning around to indoor plants be their home, working place or living space.
 
The indoor plants improve the oxygen level, keep the house air pure, remove pollutants, and also decrease the rate of indoor air pollution. They also lifts one’s mood, boosts creativity and reduces stress and depression.


\section*{Indoor plants market size and scope}

The market for indoor plants in India is estimated at over Rs 250 crores annually and is growing at 15\% to 20 \%.

Rising air pollution concerns in not only the metros but in smaller towns across the country has made indoor plant a much-needed solution for people, leading them to add more green inside their homes. Also, this has led to increased awareness of indoor plants.

The indoor plants market is segmented on the basis of type, application and product. 

\begin{enumerate}

\item On the basis of types, the indoor plants market is segmented into shade- loving plants, low light plants and high light plants.
\item On the basis of application, the indoor plants market is segmented into absorb harmful gases and home decoration.
\item On the basis of product, the indoor plants market is segmented into succulent plants, berbaceous plants, woody plants and hydroponic plants.
\end{enumerate}


\section*{Increasing Market size}
The living space of modern people has moved from outdoors to indoors more than 85\% of a persons daily life is spent indoors. Developments in information technology have allowed people to connect and remain connected to the computer environment. However, this diffusion of information technology causes a great deal of stress, such as technostress, which is a modern disease of adaptation caused by an inability to cope with the new computer technologies in a healthy manner. Many studies have been carried out to evaluate physiological and psychological effect of interacting with plants which resulted that plants relieve physiological stress and negative psychological symptoms.\\

 A contact with plants is an intuitive and non verbal activity that can provide psychological stability and comfort by stimulating four senses in various ways. Indoor plants have drawn the attention of the scientific community because of their various benefits: they enhance job satisfaction in office workers, reduce psychological stress, improve mood states, and enhance cognitive health. These effects can positively affect resistance to diseases and chronic stress.
 
Furthermore, people are increasingly viewing plants as suitable gifting options. More and more people are appreciating plants as décor items for their homes, good for the environment, and contribute to air purity. Hence, more people are viewing them as good gifting options. Also urban dwellers, surrounded by brick and mortar, yearn for greenery, even if in the form of little potters dotting their balconies or windowsills.


\section*{Trend for online sale of plants}

With the advent of e-commerce, people are looking for almost everything online. It is this broader trend that has fuelled the trend for online plants as well. Even tier 2 cities are experiencing this. In addition to the comfort and ease online shopping offers, people are frequenting visiting online nurseries for the plethora of information they offer.\\

Sometimes nursery sellers are not educated enough on the plants they're selling, or are not articulate enough to satisfy all customer queries. Therefore, online nurseries, which not only list plants, but also offer detailed information about them, prove to be a winning combination of ease-of-purchase and knowledge. Also, the working generation doesn't have the time to visit nurseries at the time they are open, leaving them with no option but to look for options online.\\

\section*{Possible business models}

The following business model are possible:

\begin{enumerate}

\item  \textbf{Aggregator Business Model:}

Aggregator Business Model is a network model where the aggregator firm collects information about particular offering providers, sign contracts with such providers, and sell their services under its own brand.

Since the aggregator is a brand, it provides an offering that has uniform quality and price, even though it is offered by different partner providers.

The offering providers never become aggregator’s employees and continue to be the owners of the product or service provided. Aggregator just helps them in marketing in a unique win-win manner.

For us it will mean that we will be having a platform which will have products listed by us by partnering with a single or only a bunch of supplier, basically selling the plants under our own brand name.


\item  \textbf{Marketplace business model:}

A marketplace is a platform where buyers and sellers interact and trade through a network.The online marketplace doesn’t own any products or services. It simply acts as a mediator and connects buyers and sellers.

In other words, a marketplace is a platform that provides value to both buyers and sellers. Sellers get a place to sell their products and grow their brand while buyers are provided with multiple choices and high-quality products all in one place.

For us it will mean that we will be having a platform which will have multiple plant sellers and buyers choosing from the listed products, where we don't own any product.

We are more interested in this model, but here we will have to become an essential part of our partners business and develop a unique selling point.

\end{enumerate}

\section*{Effect of Indoor Plants}
Multiple studies have proven that indoor plants keeps us healthier and happier, offering both psychological and physical health benefits that include:

\begin{enumerate}

\item Improving your mood

\item Reducing fatigue

\item Lowering stress and anxiety

\item Improving office performance and focus

\item Boosting healing and pain tolerance

\item Minimizing the occurrence of headaches by improving air quality

\item Easing dry skin and respiratory ailments due to dry air

\end{enumerate}


\section*{Actual Ground situation}

I along with my team visited more than 5 nurseries, and came to know that 4 of them didn't grew indoor plants on their own and just bought them from places like Pune, Kolkata and Andhra Pradesh. Only 1 nursery owner claimed to grow the plants in raipur itself.


\section*{Customer Insights}

We have conducted customer survey of 39 people, where the results were\\ 

\begin{itemize}

\item 100\% users were of 18-40 age group.

\item 66.7\% of users preferred a plant priced below Rs 500 \item 66.7\% of users buyied it from local nurseries.

\item 66.7\% buyied indoor plants for Decorative purposes. 
\item 30.8 \% buyied to reduce harmful gases, 
\item while 48.7\% buyied indoor plants because they liked to do so without any special reason.

\end{itemize}

In the survey we also asked about what problems did they faced, the results were:

\begin{itemize}

\item 66.7\% people said they don't know how to properly raise plants

\item 53.8 \% said they have lack of knowledge to choose the plants

\item 30.8\% people said they don't know there to place plants

\item 17.9\% people said they aren't able to contact the seller for complications after purchasing a plant

\item 12\% people said they don't face any problem


\end{itemize}


We also asked about their views on getting the solution:

\begin{itemize}

\item 38.5\% of the user felt that the problem must be solved.
\item 56.4\% of the people felt that the problem may be solved.
\item 5.1\% said that the problem isn't valuable to them.

\end{itemize}

\section*{About our venture}

Your venture is focused on providing counselling for selecting plants, suggestions for correct place to keep plants, plants, raw materials, real time assistance, easy accessibility, and IOT features for plant care. 


\section*{Conclusion}

With growing evidence to support the notion that plants can play an important role in providing a higher quality living environment, people are getting increasing interested in buying them. The market size of indoor plants is also growing, so, and with start of entry of big players, this is the best time to enter the market. But we will have to keep in mind that this industry comes with its own risk.





\end{document}